\chapter{Introduction}
\section{Motivation}
The internet is huge network of machines that connects large number of computers together worldwide allowing them to communicate with any other computer. The World Wide Web is an information sharing model that is built on top of the internet in which information can be accessed or manipulated easily hence experiencing dramatic growth in increased usage of internet which results in BigData. 
\\
BigData is an exponentially increasing data with high volume, high velocity with variety. This huge amount of data has intrinsic value but it’s of no use until it’s discovered \cite{bigdata}. One of the ways of finding value in BigData is analyzing it with its interrelated features such as new products, corresponding reviews, ratings and user preferences. Forming information from raw data is an entire discovery process that requires insightful analysis that would recognize patterns to predict user behaviors to recommend products.
\\
Handling BigData by manual process is very inefficient. More efficient way of processing such huge amount of data is automating the process of classifying, filtering data of user’s opinions, features, and preferences in order to understand and predict new set of related products.
\\ 
Recommender system can be defined as a tool designed to interact with large and complex information spaces to provide information or items that are relevant to the user \cite{recommeder_overview}.
\\
Nowadays recommender systems are widely used in variety of applications. Initially it applied for commercial use to analyze data. Amazon is a good example of such one of E-commerce websites. However, it is now present in several different domains including entertainment, news, books, social tags and some more sophisticated products where personalization is critical such as recipes domain. This paper would further discuss the different approaches for recipe domain to recommend healthy recipes based on user’s profile.


\pagebreak
