% Background chapter started here..
\chapter{Background}
\section{Related Work}

%There are different ways of how recommendations can be made. One of the simplest way is recommending popular products to the user. But in that case, those recommendation will be same for every user. There are well-known techniques that can make personalized recommendations.
%Recommender Systems techniques which can make personalized recommendations are normally classified into three different categories \cite{14}. Content-based Filtering, Collaborative Filtering (CF) and Hybrid Approach.\\
%Content-based filtering uses contents of the items to and information related to target user. Collaborative filtering primarily focus on set of users and their relation with items. It does not use the data about items. Collaborative filtering systems collects preferences, and with these preferences predict preference of specific user for target items. Hybrid recommender system combines two or more techniques together \cite{12}. Example, combining content-based and collaborative filtering methods in different ways. Recommender systems help in solving the problem of personalized suggestions for any product.
%\\$  $
In recent years web application development has advanced and grown. With this development food or recipe sharing applications have emerged. Hence the scope of recommender systems in food domain has increased as it is easy to get user feedback in the form of ratings, reviews or comments in the web applications.
\\
\noindent There are many reasons why recommending food or recipes are challenging. Such challenge considers changing user's mind towards their own healthy behavior. Another challenge is in predicting what people would like to eat because it depends on many factors including region, culture and demographic, to name just a few. Prior work in recommender systems includes approaches ranging from content based systems to collaborative filtering systems to hybrid approaches. 
\\

\noindent According to Mika \cite{44}, there are two types of food recommender systems present. First type considers user's preferences. It recommends recipes which are similar to the recipes liked by user in the past. Second type considers only those food items which have been identified by health care providers. It recommends recipes based on nutritional requirements for that user with no consideration of a user's preferences.
\\

\noindent The research of Freyne and Berkovsky \cite{13} uses content based technique to predict rating of unrated recipe based on the corresponding ingredients included in the recipe. For a user, the framework breaks down unrated recipe into ingredients then calculates rating of each ingredient based on rating of all other rated recipes which contain same ingredients. After calculating ratings for all ingredients of unseen recipe, framework predicts the rating of a user for the unseen recipe based on average of all rating values of all ingredients in this targeted unseen recipe. Recipes with high prediction values will be recommended.
\\

\noindent Continuation of Freyne and Berkovsky's \cite{13} work resulted in considering weighting factor for ingredients \cite{15}. This framework take a different approach by using two matrices for user features. One of them is weighted positively for rating value 4 and 5. Weighting factors for rating value 5 and 4 were 2 and 1 respectively. Contrary, another matrix weighted negatively for rating value 1 and 2. Weighting factors for rating value 2 and 1 were 1 and 2 respectively. These matrices implies strong likes and dislikes between ingredients. Based on ingredients similarity score recipes were recommended.
\\

\noindent Recent work experiment shows that how can one bring 'healthy' factor in recommendations by substituting ingredients \cite{17}.
\\
   
\noindent Other than content-based, Collaborative filtering based algorithms have also been proposed. Freyne and Berkovsky experimented with using the nearest neighbor approach (CF - KNN) on ratings. But performance of content-based approach was better. In \cite{15} a recipe recommender implemented using Singular Value Decomposition (SVD) which outperformed content-based and collaborative approach experimented by Freyne and Berkovsky.
\\

\noindent Recent developments in recipe recommender systems consider using matrix factorization. Elahi propose a food recommeder system using active learning algorithm and matrix factorization \cite{16} which collects ratings and tags in the form of feedback. This system provides human computer interaction for collecting user preferences in the form of ratings and tags. Every user and every recipe are modeled by vectors that represent their latent features. Continuation of this work resulted in incorporating calorie count \cite{18}. 
These approches performs well in predicting what user may like according to user's taste, but it did not help in changing a user's behavior towards helathy lifestyle. By incorporating calorie count we can restrict a user to choose the right food within range of their personal tastes. In this thesis, I present a   comparative analysis of recommender approaches in food domain and varying recommender approach to recommend a healthy recipes by incorporating calorie count and look to extend the work by \cite{16,18}.